
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Current Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Institute of Information Theory and Automation} % Organisation
    {Inverse Problems in Image Processing} % Project
    {} % Location
    {} % Date(s)
    {
    The project aims at developing a conceptually novel approach to inverse problems by proposing a unified theory of invariants to integral transformations using projection operators, and applying it to image restoration and classification problems in biomedical imaging and robotics. (supported by the Czech Science Foundation, 2021-23) 
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Institute of Information Theory and Automation \& Nuclear Research Centre Řež} % Organisation
    {A toolbox of measuring fuel assembly deformation using digital image processing on video recordings} % Project
    {} % Location
    {} % Date(s)
    {
    In cooperation with the Nuclear Research center Řež we developed tools to assist engineers during nuclear fuel inspection. Our toolbox is used at a Czech nuclear power plant and was also presented at EPRI - AI and Electric Power Summit. We expand the Toolbox with new functionalities using artificial intelligence and maintain the production solution.
    }


%---------------------------------------------------------
     \cventry
    {Institute of Information Theory and Automation \& Nuclear Research Centre Řež} % Organisation
    {Methods of accurate 3D wear measurement of nuclear power plant components} % Project
    {} % Location
    {} % Date(s)
    {
        The project aims to develop and experimentally verify measurements of machine components' dimensions and 3D profiles underwater exposed to a radioactive environment. We are designing a scanning device based on multiple action cameras and a line-laser projector and delivering a solution for camera communication underwater, reconstruction algorithm, and image processing pipeline. 
    }
    
%---------------------------------------------------------
  
    \cventry
    {OpenDataLab powered by Profinit and Czech Technical University} % Organisation
    {Geotrashing} % Project
    {} % Location
    {} % Date(s)
    {
       Students' eco-friendly open-source project born at the Czech government hackathon offers the optimization of a waste collection using minimum requirements. The idea was further developed as the OpenDataLab project supported by Profinit EU and Czech Technical University. The code is available at \hyperlink{https://github.com/opendatalabcz/geotrashing}{https://github.com/opendatalabcz/geotrashing}. 
    }

%---------------------------------------------------------

\end{cventries}