%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

    \cventry
    {Journal research paper} % Organisation
    {Convolutional neural network exploiting pixel surroundings of paintings} % Project
    {DOI: 10.1016/j.culher.2022.09.022} % Location
    {2022} % Date(s)
    {
    Karella, Tomáš, Jan Blažek, and Jana Striová. "Convolutional neural network exploiting pixel surroundings to reveal hidden features in artwork NIR reflectograms." Journal of Cultural Heritage 58 (2022): 186-198.
    }
    
    \cventry
    {Publication as part of interdisciplinary cooperation} % Organisation
    {Enigmatic hotspot of crayfish diversity at risk} % Project
    {DOI: 10.1002/aqc.3276} % Location
    {2020} % Date(s)
    {
        Yonvitner, Y., et al. "Enigmatic hotspot of crayfish diversity at risk: Invasive potential of non‐indigenous crayfish if introduced to New Guinea." Aquatic Conservation: Marine and Freshwater Ecosystems 30.2 (2020): 219-224.
    }
    
    \cventry
    {Publication as part of interdisciplinary cooperation} % Organisation
    {Invasive Potential of Pet-Traded Pill-Box Crabs from Genus Limnopilos} % Project
    {DOI: 10.3390/d11060091} % Location
    {2019} % Date(s)
    {
    Patoka, Jiří, et al. "Invasive potential of pet-traded pill-box crabs from genus Limnopilos." Diversity 11.6 (2019): 91.
    }

    \cventry
    {Diploma thesis} % Organisation
    {Deep Learning for MRI data} % Project
    {} % Location
    {2020} % Date(s)
    {Overview of published deep learning models for Alzheimer's disease classification (ADNI dataset). We described the drop in accuracy and identified the incorrect partitioning of the dataset. We independently confirmed the results published by Fung, Yi Ren, et al. "Alzheimer's disease brain MRI classification: Challenges and insights.". 
    }
    
    \cventry
    {Bachelor thesis} % Organisation
    {Evolutionary Algorithms for the Control of Heterogeneous Robotic Swarms} % Project
    {} % Location
    {2018} % Date(s)
    {
The goal was to use evolutionary algorithms for the behaviors of heterogeneous robotic swarms. A 2D simulation was implemented in C\#, and it was used to explore swarm controller optimization methods with the ability to create custom scenarios for robotic swarms.
    }


%---------------------------------------------------------

%---------------------------------------------------------
\end{cventries}
